\section{Background}

FHIR (Fast Health Interoperability Resources) is a standard to exchange healthcare information electronically  \cite{FHIRClinician}. FHIR offers a strong focus on  implementability in a wide variety of architectures and scenarios \cite{FHIRExecutive}. The current version of FHIR is Release 4 \cite{FHIR}.

OpenEHR is a platform focus for the development of information technology solutions for healthcare. OpenEHR provides a set of standards for models of clinical information, EHR extracts, demographic data, types of data and several types of service interfaces \cite{openEHRWhitePaper}.

\input{./texts/fhir.tex}

\input{./texts/openehr.tex}

\input{./texts/data_conversion_architecture.tex}

FHIR and openEHR share certain similarities. FHIR resources and openEHR archetypes define reusable patterns for the precise description of clinical information \cite{Bosca15}. Nevertheless, collaboration works between FHIR and openEHR communities \cite{Collaboration} could not generate resources and archetypes with matching and clinically verifiable content. One of the causes for this is different design principles utilized by both communities. The main difference being that the archetypes are expected to represent the majority of the clinical content, while the resources only contain the most common clinical information used.

The focus proposed in this work uses the StructureDefinition FHIR resources to create openEHR integration archetypes using classes CLUSTER and ELEMENT. These integration archetypes, expressed in ADL, will facilitate the data exchange between FHIR and openEHR systems. The exchange is accomplished by establishing mappings between the paths of resource elements and the paths of archetype node. Different from GENERIC\_ENTRY class, which makes no assumptions about the real form of the data, classes CLUSTER and ELEMENT represent the hierarchal structure of FHIR resources. Besides, the proposed focus uses the binding connections between information models and terminologies, supported by both standards to conserve the meaning of the exchanged data.
